Staged Abstract Interpreters

### 2018-11-18 paper/60_eval.tex
fix typo

Considering that our abstract interpreters are implemented in Scala which will be 
affected by the JIT warm up times, we run all experiments 10 times and reprot
the statistical median values of the running times.

>>>>

Considering that our abstract interpreters are implemented in Scala which will be 
affected by the JIT warm up times, we run all experiments 10 times and report
the statistical median values of the running times.
